### 2020-12-10 paper/localpsf.tex
literature review gah

@@

Wavelets [CITE ESCANDE] vs. H-matrices.

>>>>

Matrix-vector products with product-convolution approximations can be performed using the fast Fourier transform if the problem is discretized on a regular grid [CITE]. The product-convolution approximation can then replace the original operator when using Krylov methods to solve linear systems with the original operator as the coefficient operator [CITE]. However, for complex geometries, problems are rarely discretized using regular grids, so we cannot easily use the fast Fourier transform. Furthermore, in big-data inverse problems the Hessian is typically highly ill-conditioned, so the number of Krylov iterations required is large. Thus, after constructing the product-convolution approximation, it is desirable to convert the product-convolution approximation to other matrix formats that are more amenable to linear algebra operations. Wavelet compression methods have been used for this purpose [CITE WAVELETS]. Here we follow our previous work [CITE MY PAPER], in which we converting the product-convolution approximation to H-matrix format.

@@
